Map/Reduce for the common man

### 2010-02-19 doc/slides.tex
swapped slides regarding cores/network [KK]
slight change of API for map_reduce
*** empty log message ***

\begin{frame}\frametitle{}
  \begin{center}
    \includegraphics[width=\textwidth]{mrfigure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{}
  \begin{center}
    \includegraphics[width=\textwidth]{mr-new}
  \end{center}
\end{frame}

@@

\begin{frame}\frametitle{Cores \& Networks}
  Ocaml's map/reduce library works seemlessly across

  \bigskip
  \begin{itemize}
  \item multiple processor cores on the same (module \texttt{Cores})
    machine
    \begin{itemize}
    \item user just needs to specify the number of cores to be used
    \item uses Ocaml's \texttt{Unix} module
    \end{itemize}

    \bigskip
  \item networked cluster of machines (module \texttt{Network})
    \begin{itemize}
    \item user specifies the machine name(s) to be used
    \item relies on OCaml's \texttt{Unix} and \texttt{Marshal} modules
    \end{itemize}
  \end{itemize}
\end{frame}

@@

@@

  \texttt{map\_fold} takes the following forms
  \begin{ocaml}
val map_local_fold :
  map:('a -> 'b) -> fold:('c -> 'b -> 'c) -> 
  'c -> 'a list -> 'c
val map_remote_fold :
  map:('a -> 'b) -> fold:('c -> 'b -> 'c) -> 
  'c -> 'a list -> 'c
  \end{ocaml}
\end{frame}

@@

  \begin{center}
    \begin{tabular}{|l|c|c|c|c|c|}
      \hline
                 & \multicolumn{2}{|c|}{map} &
                 \multicolumn{3}{|c|}{map/fold} \\\cline{2-6}
                 & map & local & remote & ~ac~ & ~~a~~ \\\hline\hline
      \texttt{Sequential} & & & \multicolumn{3}{|c|}{(no difference)} \\\hline
      \texttt{Cores}      & & & & & \\\hline
      \texttt{Network}    & & & & & \\\hline
    \end{tabular}
  \end{center}
  % TODO: fill the cells
\end{frame}

@@

\begin{frame}\frametitle{Network}
  master and workers are the same program but distinguish using an
  environment variable (\texttt{WORKER})

@@

  \begin{enumerate}
  \item initially, each element $x_i$ in the list is a task $Map(x_i)$
  \item when a task is completed with result $r$,
    \begin{itemize}
    \item either it is $Map(x_i)$,
      \begin{itemize}
      \item if accumulator is $\texttt{Some}~v$, generate the task
        $Fold(v,r)$ and set accumulator to \texttt{None}
      \item if accumulator is \texttt{None}, push $r$ into $\mathit{stack}_r$
      \end{itemize}
    \item or it is $Fold(r',v')$
      \begin{itemize}
      \item if $\mathit{stack}_r$ is empty, the accumulator is now
        $\texttt{Some}~r$ 
      \item otherwise, pop $v$ from $\mathit{stack}_r$, and generate
        $Fold(r,v)$ 
      \end{itemize}
    \end{itemize}
  \item when done, return the accumulator
  \end{enumerate}
\end{frame}

@@

>>>>

\begin{frame}\frametitle{Google's Map/Reduce}
  \begin{center}
    \includegraphics[width=\textwidth]{mrfigure}
  \end{center}
\end{frame}

\begin{frame}\frametitle{Example}
  \begin{center}
    \includegraphics[width=0.8\textwidth]{mr-new}
  \end{center}
\end{frame}

@@

@@

\begin{frame}\frametitle{Library Options}
  % Ocaml's map/reduce library works seemlessly across

  \begin{itemize}
  \item \emph{module \texttt{Sequential}}: pure sequential evaluation
    \begin{itemize}\item 
      used as a reference
    \end{itemize}

    \bigskip
  \item \emph{module \texttt{Cores}}: multiple processor cores on the same 
    machine
    \begin{itemize}
    \item user just needs to specify the number of cores to be used
    \item only uses Ocaml's \texttt{Unix} module
    \end{itemize}

    \bigskip
  \item \emph{module \texttt{Network}}: networked cluster of machines
    \begin{itemize}
    \item user specifies the machine name(s) and number of cores on
      each machine
    \item only uses Ocaml's \texttt{Unix} module
    \end{itemize}
  \end{itemize}
\end{frame}

@@

  \texttt{map\_fold} takes the following forms
  \begin{ocaml}
val map_local_fold :
  map:('a -> 'b) -> fold:('c -> 'b -> 'c) -> 
  'c -> 'a list -> 'c

val map_remote_fold :
  map:('a -> 'b) -> fold:('c -> 'b -> 'c) -> 
  'c -> 'a list -> 'c
  \end{ocaml}
\end{frame}

@@

  map/fold is performed 
  \begin{itemize}
  \item \textcolor{orange}{locally} / \textcolor{red}{remotely}
  \end{itemize}

    \newcommand{\Lo}{\colorbox{orange}{~~}\,}
    \renewcommand{\Re}{\colorbox{red}{~~}\,}
    \newcommand{\Se}{\colorbox{blue}{~~}\,}
    \newcommand{\Pa}{\colorbox{kwblue}{~~}\,}

  \begin{center}
    \begin{tabular}{|l|c|c|c|c|c|}
      \hline
        map    & map & local & remote & ac & a 
            \\\hline\hline
      \texttt{Sequential} & \Lo & \Lo & \Lo & \Lo & \Lo \\\hline
      \texttt{Cores}   & \Re & \Re & \Re & \Re & \Re \\\hline
      \texttt{Network}    & \Re & \Re & \Re & \Re & \Re \\\hline
    \end{tabular} \\[1em]
  \end{center}

  \begin{itemize}
    \item \textcolor{blue}{sequentially} / \textcolor{kwblue}{in parallel}
  \end{itemize}

  \begin{center}
    \begin{tabular}{|l|c|c|c|c|}
      \hline
        fold    & local & remote & ac / a 
            \\\hline\hline
      \texttt{Sequential} & \Lo\Se & \Lo\Se & \Lo\Se  
            \\\hline
      \texttt{Cores}   & \Lo\Se & \Re\Se & \Re\Pa  
            \\\hline
      \texttt{Network}    & \Lo\Se & \Re\Se & \Re\Pa  \\\hline
    \end{tabular}
  \end{center}
  % TODO: fill the cells
\end{frame}

@@

\begin{frame}\frametitle{Network}
  master and workers are the same program but distinguished using an
  environment variable (\texttt{WORKER})

@@

  \begin{enumerate}
  \item initially, each element $x_i$ in the list is a task $Map(x_i)$
  \item when a task is completed with result $r$,
    \begin{itemize}
    \item either it was $Map(x_i)$,
      \begin{itemize}
      \item if accumulator is $\texttt{Some}~v$, generate the task
        $Fold(v,r)$ and set accumulator to \texttt{None}
      \item if accumulator is \texttt{None}, push $r$ into $\mathit{stack}_r$
      \end{itemize}
    \item or it was $Fold(r',v')$
      \begin{itemize}
      \item if $\mathit{stack}_r$ is empty, the accumulator is now
        $\texttt{Some}~r$ 
      \item otherwise, pop $v$ from $\mathit{stack}_r$, and generate
        $Fold(r,v)$ 
      \end{itemize}
    \end{itemize}
  \item when done, return the accumulator
  \end{enumerate}
\end{frame}

@@

\begin{frame}\frametitle{What about Map/Reduce a la Google?}
  we also provide map/reduce a la Google

  \begin{ocaml}
  val map_reduce :
    map:('v1 -> ('k2 * 'v2) list) ->
    reduce:('k2 -> 'v2 list list -> 'v2 list) ->
    'v1 list -> ('k2 * 'v2 list) list
  \end{ocaml}
\end{frame}
